**Selective DNA and Protein Isolation from Marine Macrophyte Surfaces**

### 2020-11-21 submission/manuscript.Rmd
Text formatting.

### Metaproteomics
Isolated proteins were whole trypsin digested using the FASP (filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK) according to the manufacturer's instructions with small modifications [@Wisniewski2009]. Prior to loading the solution onto the column, protein pellets were solubilized in a urea sample buffer included in the kit amended with DTT (final concentration 100 \si{\milli\Molar}) for 45 \si{\minute} at room temperature and centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to remove larger particles. The first washing step after protein solution loading was repeated twice. In addition, the centrifugation steps were prolonged if the column was clogged. Trypsin digestion was performed on column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}. The final filtrate containing peptides was acidified with 1 \si{\percent} (final concentration) trifluoroacetic acid (TFA), freezed at \num{-80} \si{\degreeCelsius}, lyophilized and sent to VIME -- Vienna Metabolomics Center (University of Vienna) for metaproteomic analysis. Peptides were re-suspended in 1 \si{\percent} (final concentration) TFA, desalted using the Pierce C18 Tips (Thermo Fisher Scientific, USA) according to the manufacturer's instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap Mass Spectrometer (Thermo Fisher Scientific, USA). Obtained MS/MS spectra were searched against a protein database composed of combined sequenced metagenomes using SEQUEST-HT engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo Fisher Scientific, USA). The target-decoy approach was used to reduce the probability of false peptide identification. Results whose false discovery rate at the peptide level was \SI{< 1}{\percent} were kept. For protein identification a minimum of two peptides and one unique peptide were required. For protein quantification, a chromatographic peak area-based free quantitative method was applied.

@@

## Figure captions
**\autoref{confocal_december}.** \nameref{confocal_december}

>>>>

### Metaproteomics
Isolated proteins were whole trypsin digested using the FASP (filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK) according to the manufacturer's instructions with small modifications [@Wisniewski2009]. Prior to loading the solution onto the column, protein pellets were solubilized in a urea sample buffer included in the kit amended with DTT (final concentration 100 \si{\milli\Molar}) for 45 \si{\minute} at room temperature and centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to remove larger particles. The first washing step after protein solution loading was repeated twice. In addition, the centrifugation steps were prolonged if the column was clogged. Trypsin digestion was performed on column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}. The final filtrate containing peptides was acidified with 1 \si{\percent} (final concentration) trifluoroacetic acid (TFA), freezed at \num{-80} \si{\degreeCelsius}, lyophilized and sent to VIME -- Vienna Metabolomics Center (University of Vienna) for metaproteomic analysis. Peptides were re-suspended in 1 \si{\percent} (final concentration) TFA, desalted using the Pierce C18 Tips (Thermo Fisher Scientific, USA) according to the manufacturer's instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap Mass Spectrometer (Thermo Fisher Scientific, USA). Obtained MS/MS spectra were searched against a protein database composed of combined sequenced metagenomes using SEQUEST-HT engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo Fisher Scientific, USA). The target-decoy approach was used to reduce the probability of false peptide identification. Results whose false discovery rate at the peptide level was < \SI{1}{\percent} were kept. For protein identification a minimum of two peptides and one unique peptide were required. For protein quantification, a chromatographic peak area-based free quantitative method was applied.

@@

## Figure legends
**\autoref{confocal_december}.** \nameref{confocal_december}
